%-------------------------
% Resume in Latex
% Author : Khaled Md Tuhidul Hossain
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{listings}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://tuhidulhossain.com/}{\Large Khaled Md Tuhidul Hossain}} & Email : \href{mailto:me@tuhidulhossain.com}{me@tuhidulhossain.com}\\
  \href{http://tuhidulhossain.com/}{https://www.tuhidulhossain.com} & Mobile : \href{tel:+65 93587649}{+65 93587649} \\
  \href{https://github.com/encryptedtouhid}{https://github.com/encryptedtouhid} &   Singapore
\end{tabular*}


%-----------SKILL-----------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}
      { C\#, Java, Javascript, C++, Python}
    \resumeSubItem{Backend Framework}
      {.NET, .NET Core , Java Spring boot, FastAPI, Django, Node Js}
    \resumeSubItem{Front-End Framework}
      {React, Angular, Vue Js, JQuery}
    \resumeSubItem{Testing Framework}
      {MSTest, xUnit.Net, JUnit, Mockito, Selenium}
    \resumeSubItem{Databases}
      {MS SQL, MySQL, Oracle, SQLite, MongoDB, CosmosDB}
    \resumeSubItem{Cloud Service}
      {AWS, Azure}
    \resumeSubItem{Miscellaneous}
      {AWS Ec2 T2, Route 53, Elastic Search, Crystal Report, PowerBI, Kubernetes, Docker, Kafka, RabbitMQ, Azure DevOps, Gitlab, Asana }
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Crédit Agricole CIB}{Pasir Panjang, Singapore}
      {Senior Software Engineer}{May 2022 - Present}
      \resumeItemListStart
        \resumeItem{Trade Finance Application}
          {Developed and maintained ASP.NET applications, optimized SQL Server queries, and created PowerBI reports, enhancing system performance and reduced all manual effort. I collaborate with global teams to develop REST APIs for trade finance using Java Spring Boot. This involves working on features like counterparty and eKYC implementation. }
        \resumeItem{Security Compliance System}
          {As a Full Stack developer, Integrated front-end and back-end systems using .NET Core, Angular, SQL Server, and Docker. Designed and implemented a batch job application for precise data synchronization using C\# (Multi-Threading \& CFT) and Control-M.}
        \resumeItem{Onboarding System}
          {Ensured conceptual completeness of technical solutions for onboarding, certification, and re-certification workflows; oversaw quality and continuous improvement of architecture; and designed new features using .NET Core, ReactJS, SQL Server, and Docker.}
        \resumeItem{DevOps}
          {Created and developed roadmap's and implementation plans, conducted comprehensive code reviews using Azure DevOps and GitLab, and managed continuous integration and delivery through Azure DevOps CI/CD pipeline.}

    \resumeItemListEnd
      
    \resumeSubheading
      {BRAC Bank Limited}{Dhaka, Bangladesh}
      {Associate Manager (Principal Software Engineer)}{Aug 2021 - April 2022}
      \resumeItemListStart
        \resumeItem{Loan Application System}
          {Implemented an advanced Loan Application Management Application with Angular, .NET Core, and Oracle DB. Resolved 350+ security hotspots and bugs flagged by SonarQube, resulting in a 40\% increase in system reliability.}
        \resumeItem{Credit Card`s Cheque payment}
          {Was in Charge of developing Credit Card`s Cheque Book payment processing feature utilizing ASP.NET and Sql server and was Accountable for devising system design and solution architecture strategies during the migration of various legacy banking projects to new technologies.}
        \resumeItem{SMS Banking Application}
          {Coordinated cross-functional teams and stakeholders to build a REST API for SMS Banking using Java Spring Boot, Apache Kafka, and Oracle DB, achieving a 30\% reduction in processing time and boosting customer satisfaction.}
        \resumeItem{Share/Stock Management Portal}
          {Developed a Share/Stock Management Portal leveraging Node.js for the backend and C++ for performance-critical components, incorporating the latest industry trends to drive innovation and enhance user experience.}
    \resumeItemListEnd

    \resumeSubheading
      {Niramoy HealthTech Limited (Startup) }{Dhaka, Bangladesh}
      {Principal Software Engineer}{Feb 2021 - Jul 2021}
      \resumeItemListStart
        \resumeItem{Electronic Health Records}
          {Ensured conceptual completeness of technical solutions and managed quality and continuous improvement of architecture to make it scalable and stable. 
          Programmed and implemented a payment gateway service for a telemedicine application using .NET Core, adhering to ISO 8583 standards. 
          Reviewed code and provided feedback relative to best practices to team members and helped everyone to improve.
          Responsible for continuous integration and delivery of the EHR application through the Azure DevOps CI/CD pipeline.}
        \resumeItem{HL7 Data Broker}
          {Developed an HL7 bidirectional broker using Java to synchronize radiology and hematology machines, enabling communication between EHR applications and PACS servers. \newline}
      \resumeItemListEnd
      \resumeSubSubheading
      {Senior Software Engineer}{May 2018 - Jan 2021}
      \resumeItemListStart
        \resumeItem{Telemedicine Web \& Mobile Application}
         {Lead a team of 8 developers working on telemedicine microservice based SaaS Application using .Net Core, Angular js, Sql Server and Java for developing android application. Additionally used Twilio SDK to develop Video Calling functionalities. Collaborated with all stakeholders including business analyst, product owners, team leads and
         SME for Innovative product design.}
        \resumeItem{Cross-Platform Prescription Application}
         {Developed \& implemented Cross-platform desktop prescription application using ElectronJs, SQLite,  Vue Js \& .Net Core Rest Api. Served 1 large govt hospital, 1000 doctor \& over ten thousand patients in 3 month.}
    \resumeItemListEnd
    
    \resumeSubheading
      {LEADS Corporation Limited}{Dhaka, Bangladesh}
      {Software Engineer}{Nov 2016 - Apr 2018}
      \resumeItemListStart
      \resumeItem{Treasury Management}
      {Developed and implemented new functionality for the Nostro and Vostro modules, and integrated Active Directory authentication using Microsoft AD services, ASP.NET WebForms (C\#), JQuery and Oracle database. Provided L3 support \& effectively resolved bugs and issues within.}
        \resumeItem{Agent Banking Solution}
          {Developed a fingerprint middleware service to standardize data from multiple fingerprint devices \& implemented EKYC, CASH IN, \& CASH OUT functionalities using .NET (C\#), AngularJs, Crystal Reports, SourceAFIS and Oracle database.}
        \resumeItem{Mobile Banking Application}
          {Developed and implemented a mobile financial application using Xamarin and  Back-End REST APIs for a reputed bank using .NET Core \& SQL SERVER . Optimized \& fixed bug for existing modules. }
      \resumeItemListEnd


      \resumeSubheading
      {Inveitco Pty Ltd (Startup)}{Dhaka, Bangladesh}
      {Software Engineer}{Mar 2015 - Feb 2016}
      \resumeItemListStart
        \resumeItem{Electronic Health Record System}
          {Implemented user interfaces for the doctor appointment module. Collaborate with the teammates, Designed and Coding RESTful APIs, enabling seamless integration with third-party services. Resolved various backend issues reported by QA and support teams, ensuring system stability and performance using Bootstrap, JQuery, PHP, CodeIgniter, MySQL.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

  %-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {American International University-Bangladesh}{Dhaka, Bangladesh}
    {Bachelor of Science in Computer Science and Engineering}{May. 2011 -- Feb. 2016}   
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{High-Frequency Trading (HFT) Engine}
      {A sophisticated software system designed to execute a large number of financial transactions at extremely high speeds using C\#.}
    \resumeSubItem{LLTS-Engine}
      {A basic Low Latency Trading Engine  built with C++.}
    \resumeSubItem{Data Streaming Platform}
      {A streaming platform  built with Java Spring Boot , Apache Kafka,  React which is capable of  stream videos and audio files.}
    \resumeSubItem{CXCommenter}
      {A Visual Studio Extension for Automatic XML Commenting using C\#.}
    \resumeSubItem{CpuGuard.NET}
      {CPU Usage Control for ASP.NET Core Applications NuGet package  built with C\#.}
  \resumeSubHeadingListEnd


%-----------Publications-----------------
\section{Publications}
\resumeSubHeadingListStart
  \resumeSubItem{OTR: A Transparent database approach for using ontology in information systems}
    {\newline AIUB Journal of Science and Engineering (AJSE) vol. 14, no. 1 · Aug 1, 2015.}
\resumeSubHeadingListEnd

% --------PROGRAMMING SKILLS------------
% \section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: C\# , Java , Python , Javascript, C++}
%      \hfill
%      \textbf{Framework}{: .NET Core , Spring boot, Django, Node Js}
%    }
%    \item{
%      \textbf{Frontend}{: React, Angular, Vue Js, JQuery}
%      \hfill
%      \textbf{Testing}{: MSTest, xUnit.Net, JUnit, Mockito, Selenium}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}