%-------------------------
% Resume in Latex
% Author : Khaled Md Tuhidul Hossain
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{listings}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://tuhidulhossain.com/}{\Large Khaled Md Tuhidul Hossain}} & Email : \href{mailto:me@tuhidulhossain.com}{me@tuhidulhossain.com}\\
  \href{http://tuhidulhossain.com/}{https://www.tuhidulhossain.com} & Mobile : \href{tel:+65 93587649}{+65 93587649} \\
  \href{https://github.com/encryptedtouhid}{https://github.com/encryptedtouhid} &   Singapore
\end{tabular*}


%-----------SKILL-----------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}
      { Python, C\#, Java, Javascript, TypeScript, C++ }
    \resumeSubItem{Backend Framework}
      {FastAPI, Django, .NET, .NET Core , Java Spring boot,  Node Js, KMDF {\&} UMDF Framework}
    \resumeSubItem{Front-End Framework}
      {React, Angular, Vue Js, JQuery}
    \resumeSubItem{Testing Framework}
      {MSTest, xUnit.Net, JUnit, Mockito, Selenium}
    \resumeSubItem{Databases}
      {MS SQL, MySQL, Oracle, SQLite, MongoDB, CosmosDB}
    \resumeSubItem{Cloud Service}
      {AWS, Azure}
    \resumeSubItem{Miscellaneous}
      {AWS Ec2 T2, Route 53, Elastic Search, Azure AI Search, AWS AI Services, Crystal Report, PowerBI, Kubernetes, Docker, Kafka, RabbitMQ, Azure DevOps, Gitlab, Asana }
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {GIC Private Limited}{Robinson Road, Singapore}
    {Senior Software Engineer}{Oct 2024 - Present}
    \resumeItemListStart
      \resumeItem{}
        {Spearheaded the design and delivery of PEII Project, managing cross-functional teams to implement end-to-end solutions for trading and portfolio management operations using Python and ReactJS.}
      \resumeItem{}
        {Lead the implementation of end-to-end data analytics and AI services for Private Equity products/platforms, utilizing technologies such as Python, DelphiX, AWS (SageMaker, Lambda) to deliver advanced data insights, Document Summarization, and optimize report generation processes.} 
      \resumeItem{}
        {Provided architectural guidance to ensure scalability and performance, mentoring junior developers and fostering technical growth.}   
    \resumeItemListEnd

    \resumeSubheading
      {Crédit Agricole CIB}{Pasir Panjang, Singapore}
      {Senior Software Engineer}{May 2022 - Sep 2024}
      \resumeItemListStart
        \resumeItem{}
        {Lead the software development lifecycle from design to deployment and implemented high-performance, scalable, and reliable solutions that were suited for trade banking, security compliance and crucial applications, guaranteeing smooth operation and conformity to legal requirements using .NET Core and ReactJS. }
        \resumeItem{}
        {As a Full Stack developer, Integrated front-end and back-end systems using .NET Core, Angular, SQL Server, and Docker. Designed and implemented a batch job application for precise data synchronization (Multi-Threading \& CFT) using C\# and Control-M. I collaborate with global teams to develop REST APIs for trade finance using Java Spring Boot \& ReactJs.}
        \resumeItem{}
        {Led code reviews and process optimization for the Workflow Application, improving efficiency by 40\%, and mentored junior developers for assigned projects.}
        \resumeItem{}
        {Authored thorough code documentation, architecture diagrams, and technical requirements to facilitate effective teamwork and information exchange. Oversaw and configured CI/CD pipelines using Azure DevOps, and made sure that scalable, high-quality solutions were delivered.}
        \resumeItem{}
        {Collaborated with cross-functional teams (business, design, product) to ensure strategic alignment and seamless integration, providing clear updates on project status, technical decisions, and goals to stakeholders.}

    \resumeItemListEnd
      
    \resumeSubheading
      {BRAC Bank Limited}{Dhaka, Bangladesh}
      {Associate Manager}{Aug 2021 - April 2022}
      \resumeItemListStart
        \resumeItem{}
          {Took full ownership of the end-to-end delivery of software systems, ensuring the expected quality is achieved while adhering to schedule and budget constraints.}
        \resumeItem{}
          {Was Accountable for devising system design and solution architecture strategies during the migration of various legacy banking projects to new technologies. Also developed and optimized complex SQL queries, stored procedures, user-defined functions, and views for enhanced database performance and functionality.}
        \resumeItem{}
        {Ensured efficient operations, including service requests, technical support, incident, and problem management, while maintaining system availability for critical enterprise banking applications such as Cash Management, Internet Banking, Loan Application Management, and Document Management.}
        \resumeItem{}
        {Managed and guided a team of software developers and business analysts to deliver efficient solutions, while supporting managers and senior managers with strategic insights and operational alignment to achieve business objectives.}
        \resumeItem{}
          {Maintained effective communication with vendors to ensure seamless collaboration and issue resolution.}
        \resumeItem{}
          {Coordinated cross-functional teams and stakeholders to build a REST API for SMS Banking using Java Spring Boot, Apache Kafka, and Oracle DB, achieving a 30\% reduction in processing time and boosting customer satisfaction.}
        \resumeItem{}
        {Led reporting, escalation processes, and stakeholder communication, ensuring timely identification, prioritization, and resolution of critical issues(L2,L3) to maintain operational efficiency and meet business objectives.}
    
      \resumeItemListEnd

   \resumeSubheading
      {Niramoy HealthTech Limited (Startup) }{Dhaka, Bangladesh}
      {Principal Software Engineer}{Feb 2021 - Jul 2021}
      \resumeItemListStart
        \resumeItem{}
          {Led and mentored an 8-member developer team, guiding design, development, and deployment of key solutions for Telemedicine and EHR platforms, fostering a culture of continuous improvement, innovation, and best practices adherence in coding, testing, and deployment.}
        \resumeItem{}
          {Designed scalable, maintainable architecture for EHR and Telemedicine apps, ensuring technical solutions' completeness, focusing on robust, stable systems for future growth, led architecture discussions for long-term scalability, maintainability, and performance considerations.}
        \resumeItem{}
          {Managed reporting, escalations, and stakeholder communication for prompt action, led strategic development and deployment of EHR and telemedicine plans, collaborated with executives to align initiatives with organizational goals for success.}    
      \resumeItem{}
          {Managed relationships with key stakeholders, including business, design, and product teams, coordinated technical and business discussions to align project goals, ensuring technical decisions supported business objectives and customer needs.}
      \resumeItemListEnd
      \resumeSubSubheading
      {Senior Software Engineer}{May 2018 - Jan 2021}
      \resumeItemListStart
        \resumeItem{}
         {Lead a team of 8 developers working on telemedicine microservice based SaaS Application using .Net Core, Angular js, Sql Server and Java for developing android application. Additionally used Twilio SDK to develop Video Calling functionalities. Collaborated with all stakeholders including business analyst, product owners, team leads and
         SME for Innovative product design.}
        \resumeItem{}
         {Developed \& implemented Cross-platform desktop prescription application using ElectronJs, SQLite,  Vue Js \& .Net Core Rest Api. Served 1 large govt hospital, 1000 doctor \& over ten thousand patients in 3 month.}
    \resumeItemListEnd
    
    \resumeSubheading
      {LEADS Corporation Limited}{Dhaka, Bangladesh}
      {Software Engineer}{Nov 2016 - Apr 2018}
      \resumeItemListStart
      \resumeItem{}
      {Developed and implemented new functionality for the Nostro and Vostro modules, and integrated Active Directory authentication using Microsoft AD services, ASP.NET WebForms (C\#), JQuery and Oracle database. Provided L3 support \& effectively resolved bugs and issues within.}
        \resumeItem{}
          {Developed a fingerprint middleware service to standardize data from multiple fingerprint devices \& implemented EKYC, CASH IN, \& CASH OUT functionalities using .NET (C\#), AngularJs, Crystal Reports, SourceAFIS and Oracle database.}
        \resumeItem{}
          {Developed and implemented a mobile financial application using Xamarin and  Back-End REST APIs for a reputed bank using .NET Core \& SQL SERVER . Optimized \& fixed bug for existing modules. }
      \resumeItemListEnd


      \resumeSubheading
      {Inveitco Pty Ltd (Startup)}{Dhaka, Bangladesh}
      {Software Engineer}{Mar 2015 - Feb 2016}
      \resumeItemListStart
        \resumeItem{}
          {Implemented user interfaces for the doctor appointment module. Collaborate with the teammates, Designed and Coding RESTful APIs, enabling seamless integration with third-party services. Resolved various backend issues reported by QA and support teams, ensuring system stability and performance using Bootstrap, JQuery, PHP, CodeIgniter, MySQL.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

  %-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {American International University-Bangladesh}{Dhaka, Bangladesh}
    {Bachelor of Science in Computer Science and Engineering}{May. 2011 -- Feb. 2016}   
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{Blog Application}
%       {Blog Engine Developed With Blazor {\&} .NET 8.0.}
%     \resumeSubItem{Fetch Web Pages CLI}
%       {Implemention of a command line program that can fetch web pages and saves them to disk for later retrieval and browsing using Python {\&} Docker.}
%     \resumeSubItem{CXCommenter}
%       {A Visual Studio Extension for Automatic XML Commenting using C\#.}
%     \resumeSubItem{CpuGuard.NET}
%       {CPU Usage Control for ASP.NET Core Applications NuGet package  built with C\#.}
%     \resumeSubItem{High-Frequency Trading (HFT) Engine}
%       {A sophisticated software system designed to execute a large number of financial transactions at extremely high speeds using C\#.}
%     \resumeSubItem{LLTS-Engine}
%       {A basic Low Latency Trading Engine  built with C++.}
%     \resumeSubItem{Data Streaming Platform}
%       {A streaming platform  built with Java Spring Boot , Apache Kafka,  React which is capable of  stream videos and audio files.}
%   \resumeSubHeadingListEnd


%-----------Publications-----------------
\section{Publications}
\resumeSubHeadingListStart
  \resumeSubItem{OTR: A Transparent database approach for using ontology in information systems}
    {\newline AIUB Journal of Science and Engineering (AJSE) vol. 14, no. 1 · Aug 1, 2015.}
\resumeSubHeadingListEnd

% --------PROGRAMMING SKILLS------------
% \section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: C\# , Java , Python , Javascript, C++}
%      \hfill
%      \textbf{Framework}{: .NET Core , Spring boot, Django, Node Js}
%    }
%    \item{
%      \textbf{Frontend}{: React, Angular, Vue Js, JQuery}
%      \hfill
%      \textbf{Testing}{: MSTest, xUnit.Net, JUnit, Mockito, Selenium}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}